Positivity-Preserving Adaptive Runge-Kutta Methods

### 2020-02-18 latex/overview.tex
Added convergence plots for Diffusion problem and Advection-Decay problem
overview.ipynb:
Added Plots and descriptions 

utils.py:
Made output more clear if solver failed

plots/Convergence.ipynb:
Notebook to compute and plot convergence

@@

When tested on the diffusion equation with an spike as initial data the $b$ is only changed for the first step. The change of the $b$ can lead to reasonable changes of the hight of the maximum.

>>>>

As test problem the PDE
\begin{equation}
\frac{\partial u}{\partial t} = -a \frac{\partial u}{\partial z} - K (u)
\end{equation}
is simulated with the method of lines on the domain $x = [0,1]$ with $N =100$ points. The Problem consists of a Advection part and an Exponential decay. At $x =0$ a inflow boundary with $u(0,t)=1$ is used. The initial condition is $u(x,0)=0$
As semidiscretization an upwinding scheme is used. This leads to positivity preserving ODE
\begin{equation}
\frac{\mathrm d}{\mathrm d t} u_i = \frac{a}{\Delta x} \left( u_{i-1} - u_i \right) - K u_{i-1}
\end{equation}
The parameters are set to $a=1$ and $K=1$.
For $\dt \leq 0.0082$ the unaltered method lead to positive solutions. For larger $\dt$ the original method leads to negative values and $b$ is altered. For $\dt >0.016$ the dp5 is no longer stable.
In Figure\,\ref{fig:conv_expl} the convergence is plotted for the altered and unaltered method.

\begin{figure}[h]
\centering
\includegraphics[scale=0.75]{plots/conv_adde.pdf}
\caption{Convergence adapted dp5}
\label{fig:conv_expl}
\end{figure}

@@

The method is tested on the diffusion equation 
\begin{equation}
\frac{\partial }{\partial t} = D \frac{\partial^2}{\partial x^2}
\end{equation}
with homogeneous Dirichlet boundary conditions on the domain $x = [-0.5,0.5]$ with $N=100$ points. The equation is semidiscreticed using the 3-point-scheme
\begin{equation}
\frac{\mathrm d}{\mathrm d t} u_i = \frac{d}{\Delta x^2} \left( u_{i-1} - 2u_i + u_{i+1} \right)
\end{equation}
As initial condition $u^0 = (0,\cdots,0,1,0,\cdots,0)^T$ is used. The diffusion coefficient is$D=1$
The ODE is solved using the implicit EX3 method. 
For large (Note: better word for 'not small enough') $\dt$ the method computes negative values for $u^1$.
These can be corrected by adapting the $b$. 
If the direct adaptation approach is used the $u^1$ can show gliches/is nonphysical. 
Alternatively the convex combination approach is used. A first order embedded method is added. The $u^1$ computed with the convex combination are physical.
For both approaches the remaining steps can be computed with the standard $b$.

In figure\,\ref{fig:conv_impl} the convergence is shown. For $\dt < \num{3e-5} $ the standard $b$ yields to a positive result. For larger $\dt$ the $b$ have to be adapted to ensure positivity.
The EX3a shows similar convergence properties than the original method. 
The EX3c has larger errors than the EX3a but leads to physical solutions for all time-steps. 
\begin{figure}[h]
\centering
\includegraphics[scale=0.75]{plots/conv_heat.pdf}
\caption{Convergence adapted ex3}
\label{fig:conv_impl}
\end{figure}
